---
title: "DSjobtracker - Data visualisation"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(DSjobtracker)
library(ggplot2)
library(plotly)
library(tidyverse)
library(magrittr)
library(packrat)
library(here)
library(viridis)
```
```



# Advertisements

Column {data-width=800}
-----------------------------------------------------------------------
#### Countrywise composition of number of Statistical Job Advertistments 
```{r}
devtools::install_github("thiyangt/DSjobtracker")
library(DSjobtracker)
library(maps)
library(viridis)
library(mapproj)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(tidyr)
library(ggrepel)
library(plotly)
library(R.utils)

#Importing the data sets

data("DStidy")
data<-map_data("world")
worlddata<-data.frame(world.cities)

#Taking to same consistency

worlddata[worlddata=="USA"]<-"United States"
worlddata[worlddata=="UK"]<-"United Kingdom"


#Making a frequency table of vacanvies for the countries


summaries<-as.data.frame(table(DStidy$Job_Country))
colnames(summaries)<-c("country.etc","Frequency")


#Making to lower case

summaries$country.etc<-str_to_lower(summaries$country.etc)
worlddata$country.etc<-str_to_lower(worlddata$country.etc)


#Filtering the needed countries

datall<-worlddata %>% filter(country.etc%in%summaries$country.etc)

#Joining the needed countries and Frequencies

dup_data_joined<-left_join(datall,summaries)

#Extracting a special row for a country in Canada
special_row<-dup_data_joined[dup_data_joined$name=="Edmonton",]
data_joined<-dup_data_joined[!duplicated(dup_data_joined[,c("country.etc")]),]

#Removing the row for Canada and pasting the special row
data_joined<-data_joined[-c(10),]
data_joined<-rbind(data_joined,special_row)

#Making the Countries to upper case letters
data_joined$country.etc<-capitalize(data_joined$country.etc,collapse=" ")
data_joined[data_joined=="Sri lanka"]<-"Sri Lanka"
data_joined[data_joined=="United states"]<-"United States"
data_joined[data_joined=="United kingdom"]<-"United Kingdom"
data_joined[data_joined=="new zealand"]<-"New Zealand"
data_joined[data_joined=="United arab emirates"]<-"United Arab Emirates"
data_joined[data_joined=="New caledonia"]<-"New Caledonia"

#Entering a new column with a text

data_joined<-data_joined%>%
  arrange(Frequency)%>%
  mutate(name=factor(country.etc,unique(country.etc)))%>%
  mutate(mytext=paste("Country: ",name,"\n","Number of Job Advertistments: ",Frequency,sep = ""))



#Plotting the map
plot<-data_joined%>%
  ggplot() +
  geom_polygon(data = data, aes(x=long, y = lat, group = group), fill="grey", alpha=0.9) +
  geom_point( data=data_joined, aes(x=long, y=lat,color=Frequency, text=mytext),size=4) +
   
  scale_color_viridis() +geom_text_repel(data=data_joined %>% arrange(Frequency),aes(x=long,y=lat,label=country.etc),size=3)+
  theme_void() + coord_map()
ggplotly(plot,tooltip = "text")
```


Column {data-width=350}{.tabset .tabset-fade}
-----------------------------------------------------------------------
### C1

```{r}
p <- ggplot(data_joined, aes(x = reorder(country.etc,Frequency), y = Frequency,text=paste("Number of Job Advertistments: ",Frequency)))+
  geom_col( width = 0.7,fill="steelblue")+coord_flip()+ylab("Number of Job Advertistements")+xlab("Country")
ggplotly(p,tooltip="text")


```



# Software

Column {data-width=500}
-----------------------------------------------------------------------

### Statistical Software

```{r, comment=NA, warning=FALSE, include=FALSE}
data(DStidy)
head(DStidy)
```

```{r, comment=NA, warning=FALSE, include=FALSE}
DStidy$Statistical_software <- paste(DStidy$R,DStidy$SAS,DStidy$SPSS,DStidy$Python,DStidy$MAtlab,sep = "::")

unique(DStidy$Statistical_software)

d1 <- DStidy$Statistical_software %>% table() %>% as.data.frame()
names(d1) <- c('Statistical_software', 'Frequency')
d1 <- d1[order(d1$Frequency, decreasing = T),]

d1
```

```{r, comment=NA, warning=FALSE, include=FALSE}
DStidy$Statistical_software[DStidy$Statistical_software=="1::0::0::1::0"] <-"R & Python"
DStidy$Statistical_software[DStidy$Statistical_software=="0::0::0::0::0"] <-"No Statistical softwares"
DStidy$Statistical_software[DStidy$Statistical_software=="0::0::0::1::0"] <-"Python only"
DStidy$Statistical_software[DStidy$Statistical_software=="1::1::0::1::0"] <-"R, SAS & Python only "

DStidy$Statistical_software[DStidy$Statistical_software=="0::1::0::0::0"] <-"SAS only"

DStidy$Statistical_software[DStidy$Statistical_software=="1::0::0::0::0"] <-"R only"

DStidy$Statistical_software[DStidy$Statistical_software=="1::0::0::1::1" | DStidy$Statistical_software=="0::1::1::0::0"| DStidy$Statistical_software=="1::1::1::1::0"| DStidy$Statistical_software=="1::1::1::1::1"| DStidy$Statistical_software=="1::1::0::0::0"| DStidy$Statistical_software=="1::0::1::0::0"| DStidy$Statistical_software=="0::1::0::1::0"| DStidy$Statistical_software=="1::1::1::0::1"| DStidy$Statistical_software=="1::0::1::1::1"| DStidy$Statistical_software=="1::0::1::1::0"| DStidy$Statistical_software=="1::1::1::0::0"| DStidy$Statistical_software=="1::1::0::1::1"| DStidy$Statistical_software=="1::1::0::0::1"| DStidy$Statistical_software=="0::1::0::1::1"| DStidy$Statistical_software=="0::0::1::0::0"| DStidy$Statistical_software=="1::0::0::0::1"| DStidy$Statistical_software=="0::0::0::1::1"] <-"Other Statistical software"

unique(DStidy$Statistical_software)

d1 <- DStidy$Statistical_software %>% table() %>% as.data.frame()
names(d1) <- c('Statistical_software', 'Frequency')
d1 <- d1[order(d1$Frequency, decreasing = T),]

d1

```

```{r}
d1 <- DStidy$Statistical_software %>% table() %>% as.data.frame()
names(d1) <- c('Statistical_software', 'Frequency')
d1 <- d1[order(d1$Frequency, decreasing = T),]


plot1 <- ggplot(d1, aes(x= reorder(Statistical_software, Frequency), y=Frequency))+ labs(y="Number of advertisements", x="") + geom_bar(stat = "identity", width = 0.5, fill ="#FC4E07") +coord_flip()

ggplotly(plot1)
```

Column {data-width=500}
-----------------------------------------------------------------------

### Programming software

```{r, comment=NA, warning=FALSE, include=FALSE}
DStidy$Programming_software <- paste(DStidy$Spark,DStidy$Scala,DStidy$Java,DStidy$C,DStidy$C.,DStidy$C..,DStidy$pyspark,sep = "::")



d2 <- DStidy$Programming_software%>% table() %>% as.data.frame()
names(d2) <- c('Programming_software', 'Frequency')
d2 <- d2[order(d2$Frequency, decreasing = T),]

d2
```

```{r, comment=NA, warning=FALSE, include=FALSE}
DStidy$Programming_software[DStidy$Programming_software=="0::0::0::0::0::0::0"] <-"No programming software"
DStidy$Programming_software[DStidy$Programming_software=="1::0::0::0::0::0::0"] <-"Spark only"
DStidy$Programming_software[DStidy$Programming_software=="0::0::1::0::0::0::0"] <-"Java only"
DStidy$Programming_software[DStidy$Programming_software=="0::1::0::0::0::0::0"] <- "Scala only" 
DStidy$Programming_software[DStidy$Programming_software=="0::0::0::0::0::1::0"| DStidy$Programming_software=="1::1::0::0::0::0::0" | DStidy$Programming_software=="0::0::0::0::0::0::1"| DStidy$Programming_software=="0::0::0::1::0::0::0"| DStidy$Programming_software=="0::1::1::0::0::1::0"| DStidy$Programming_software=="1::0::1::0::0::0::0"| DStidy$Programming_software=="1::1::1::0::0::0::0"| DStidy$Programming_software=="0::0::1::0::0::1::0"| DStidy$Programming_software=="0::1::1::0::0::0::0"| DStidy$Programming_software=="0::0::1::1::0::0::0"| DStidy$Programming_software=="1::0::1::1::0::1::0"| DStidy$Programming_software=="0::0::0::1::0::0::1"|DStidy$Programming_software=="0::0::1::0::1::0::0"|DStidy$Programming_software=="0::0::1::1::0::1::0"|DStidy$Programming_software=="0::1::0::0::0::1::0"|DStidy$Programming_software=="1::0::1::0::0::0::1"|DStidy$Programming_software=="1::0::1::0::0::1::0"|DStidy$Programming_software=="1::1::0::0::0::0::1"|DStidy$Programming_software=="1::1::1::0::0::1::0"|DStidy$Programming_software=="1::1::1::0::1::0::0"] <-"Other programmimg software"

d2 <- DStidy$Programming_software%>% table() %>% as.data.frame()
names(d2) <- c('Programming_software', 'Frequency')
d2 <- d2[order(d2$Frequency, decreasing = T),]

d2

```

```{r}
plot2 <- ggplot(d2, aes(x= reorder(Programming_software, Frequency), y=Frequency))+ labs(y="Number of advertisements", x="") + geom_bar(stat = "identity", width = 0.5, fill ="#009E73") +coord_flip()

ggplotly(plot2)
```


### Database software and Query languages

```{r, comment=NA, warning=FALSE, include=FALSE}
DStidy$database_softwares_and_query_languages <- paste(DStidy$OLE_DB,DStidy$SQL,DStidy$NoSQL,DStidy$MySQL,DStidy$RDBMS,DStidy$MongoDB,DStidy$Hadoop,sep = "::")

unique(DStidy$database_softwares_and_query_languages)

d3 <- DStidy$database_softwares_and_query_languages%>% table() %>% as.data.frame()
names(d3) <- c('database_softwares_and_query_languages', 'Frequency')
d3 <- d3[order(d3$Frequency, decreasing = T),]

d3
```

```{r, comment= NA, warning=FALSE, include=FALSE}
DStidy$database_softwares_and_query_languages[DStidy$database_softwares_and_query_languages=="0::0::0::0::0::0::0"] <-"No database software and/or query language"
DStidy$database_softwares_and_query_languages[DStidy$database_softwares_and_query_languages=="0::1::0::0::0::0::0"] <-"SQL only"
DStidy$database_softwares_and_query_languages[DStidy$database_softwares_and_query_languages=="0::1::0::1::0::0::0"] <-"SQL & MySQL only"
DStidy$database_softwares_and_query_languages[DStidy$database_softwares_and_query_languages=="0::1::0::0::0::0::1"] <-"SQL & Handoop only"
DStidy$database_softwares_and_query_languages[DStidy$database_softwares_and_query_languages=="0::1::1::0::0::0::0"] <-"SQL & NoSQL only"

DStidy$database_softwares_and_query_languages[DStidy$database_softwares_and_query_languages=="0::0::0::1::0::0::0" | DStidy$database_softwares_and_query_languages=="0::0::0::0::0::0::1"| DStidy$database_softwares_and_query_languages=="0::1::0::1::0::0::1" | DStidy$database_softwares_and_query_languages=="0::0::0::0::1::0::0"| DStidy$database_softwares_and_query_languages=="0::1::0::0::0::1::0"| DStidy$database_softwares_and_query_languages=="0::1::0::0::0::1::1"| DStidy$database_softwares_and_query_languages=="0::1::0::0::1::0::1"| DStidy$database_softwares_and_query_languages=="1::1::0::0::0::0::0"| DStidy$database_softwares_and_query_languages=="0::0::1::0::0::0::0"| DStidy$database_softwares_and_query_languages=="0::0::1::0::1::0::1"| DStidy$database_softwares_and_query_languages=="0::1::0::0::1::0::0"| DStidy$database_softwares_and_query_languages=="0::1::1::0::0::0::1"| DStidy$database_softwares_and_query_languages=="0::1::1::0::1::0::0"|DStidy$database_softwares_and_query_languages=="0::1::1::0::1::0::1"|DStidy$database_softwares_and_query_languages=="0::1::1::1::0::0::0"| DStidy$database_softwares_and_query_languages=="0::1::0::1::1::0::1"| DStidy$database_softwares_and_query_languages=="0::1::0::1::1::0::0"| DStidy$database_softwares_and_query_languages=="0::0::0::0::0::1::1"] <-"Other"

unique(DStidy$database_softwares_and_query_languages)

d3 <- DStidy$database_softwares_and_query_languages %>% table() %>% as.data.frame()
names(d3) <- c('database_softwares_and_query_languages', 'Frequency')
d3 <- d3[order(d3$Frequency, decreasing = T),]

d3
```


```{r}
plot3 <- ggplot(d3, aes(x= reorder(database_softwares_and_query_languages, Frequency), y=Frequency))+ labs(y="Number of advertisements", x="") + geom_bar(stat = "identity", width = 0.5, fill ="#56B4E9") +coord_flip()

ggplotly(plot3)
```


