---
title: "Data Visualisation"
author: "W.D.M FERNANDO"
date: "2 September 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Figure 01

```{r,include=FALSE}

library(readxl)
DSS<-read_excel("DSS.xlsx")
str(DSS)
unique(DSS$Consultant)
DSS <- DSS[!is.na(DSS$Consultant),]
DSS
```

```{r,include=FALSE}

DSS[(is.na(DSS$Job_title)), ]
DSS1 <- DSS[!(DSS$Consultant=="Thiyanga"),]
DSS1

```

```{r,include=FALSE}
library(tidyverse)
Job_Titles <- str_to_lower(DSS1$Job_title)
Job_Titles
Job_Titles1 <- str_replace_all(Job_Titles,",", " ") 
Job_Titles1 
Job_Titles2 <- str_replace_all(Job_Titles1,"/", " ")  
Job_Titles2 
Job_Titles3 <- str_replace_all(Job_Titles2,"-", " ") 
Job_Titles3 
Job_Titles4 <- str_replace_all(Job_Titles3,"#", " ") 
Job_Titles4 
Job_Titles5 <- str_replace_all(Job_Titles4,"data scientist","Data Scientist")  
Job_Titles5 
Job_Titles6 <- str_replace_all(Job_Titles5,"Data Scientists","Data Scientist")  
Job_Titles6
Job_Titles7 <- str_replace_all(Job_Titles6,"analytics", " Analyst")  
Job_Titles7
Job_Titles8 <- str_replace_all(Job_Titles7,"data analyst", " Data Analyst")
Job_Titles8
Job_Titles9 <- str_replace_all(Job_Titles8,"data engineer", " Data Engineer")
Job_Titles9
```

```{r,include=FALSE}
A<-table(Job_Titles9)
A
```

```{r,include=FALSE}
AA<-as.data.frame(A)
AA
other<-filter(AA,Freq <=5)
other
str(other)
```


```{r,include=FALSE}
a<-filter(AA,Freq==62)
a
b<-filter(AA,Freq==16)
b
c<-filter(AA,Freq==115)
c
d<-filter(AA,Freq==12)
d
e<-filter(AA,Freq==10)
e

```


```{r,include=FALSE}
D<-data.frame(Job_Type =c('Data Scientist','Data Analyst','Data Engineer','Senior Data Scientist','Junior Data Scientist','Other'),Frequency=c(115,62,16,10,12,173))

```

```{r,echo=FALSE}
library(knitr)
kable(D)
library(ggplot2)
ggplot(D,aes(x=Job_Type,y=Frequency)) +geom_bar(position="dodge",stat="identity",width = 0.75)+ggtitle("Bar Graph of Required Job Titles")+scale_x_discrete(
    limits=c("Senior Data Scientist","Junior Data Scientist","Data Engineer","Data Analyst","Data Scientist","Other"),
    labels=c("Senior Data Scientist","Junior Data Scientist","Data Engineer","Data Analyst","Data Scientist","Other") 
    ) +coord_flip() 
```

**We can conclude that based on the above bar graph mostly required job title is 'Data Scientist'.**

###Figure 02

**Word Cloud of Job Titles**

```{r,echo=FALSE,message=FALSE,warning=FALSE}
library(tidyverse)
library(treemapify)
library(readxl)
library(ggplot2)
library(reshape2)
library(plyr)
library(tm)
library(SnowballC)
library(wordcloud)
library(wordcloud2)
library(RColorBrewer)

cnames<-data.frame(Job_Titles9)

docs<-Corpus(VectorSource(cnames))
for (j in seq(docs))
{
  docs[[j]] = gsub("(RT|via)((?:\\b\\W*@\\w+)+)", "", docs[[j]])
  docs[[j]] = gsub("@\\w+", "", docs[[j]])
  docs[[j]] = gsub("http\\w+", "", docs[[j]])
  docs[[j]] = gsub("[ \t]{2,}", "", docs[[j]])
  docs[[j]] = gsub("^\\s+|\\s+quot;", "", docs[[j]])
  docs[[j]] = gsub("[^\x20-\x7E]", "", docs[[j]])
}
skipwords = c(stopwords("english"), "system","technology")

kb.tf <- list(weighting = weightTf, stopwords  = skipwords,
              removePunctuation = TRUE,
              tolower = TRUE,
              minWordLength = 4,
              removeNumbers = TRUE, stripWhitespace = TRUE,
              stemDocument= TRUE)
docs <- tm_map(docs, PlainTextDocument) 
tdm = TermDocumentMatrix(docs, control = kb.tf)
tdm = as.matrix(tdm)
word_freqs = sort(rowSums(tdm), decreasing=TRUE)
dm = data.frame(word=names(word_freqs), freq=word_freqs)
set.seed(1234)
p <- ggplot(subset(dm, freq>10), aes(word, freq))
p <-p+ geom_bar(stat="identity")
p <-p+ theme(axis.text.x=element_text(angle=60, hjust=5))


wordcloud2(dm, minRotation = -pi/20, maxRotation = -pi/20, minSize = 0.005,
           rotateRatio = 0.5,ellipticity = 0.4, fontFamily = 'Segoe UI',size = 7,fontWeight = "bold",color = "random-light", backgroundColor = "rose")


```

**Above word cloud illustrates that 'Data Scientist','Data Analysit','Data Engineer',Senior Data Analyst','Junior Data Scientist' are the mostly required job tites.**

###Figure 03

```{r,include=FALSE}
library(tidyverse)
library(ggplot2)
library(readr)
library(maps)
library(viridis)
```
```{r,include=FALSE}
library(tidyverse)
Location <- DSS1[!is.na(DSS1$Location),]

location1 <- str_replace_all(DSS1$Location,"Colombo", "SL") 
location1
location2 <- str_replace_all(location1,"San Fransico", "USA") 
location2
location3 <- str_replace_all(location2,"Montgomery Country", "USA") 
location3
location4 <- str_replace_all(location3,"new kensington", "USA") 
location4
location5 <- str_replace_all(location4,"Arlington", "USA") 
location5
location6 <- str_replace_all(location5,"Cambridge", "USA") 
location6
location7 <- str_replace_all(location6,"Boise", "USA") 
location7
location8 <- str_replace_all(location7,"Mclean", "USA") 
location8
location9 <- str_replace_all(location8,"Seattle", "USA") 
location9
location10 <- str_replace_all(location9,"Minneapolis", "USA") 
location10
location11 <- str_replace_all(location10,"Salt Lake City", "USA") 
location11 
location12 <- str_replace_all(location11,"Mountain View", "USA") 
location12
location13 <- str_replace_all(location12,"New York", "USA") 
location13
location14 <- str_replace_all(location13,"Washington", "USA") 
location14
location15 <- str_replace_all(location14,"Chicago", "USA") 
location15
location16 <- str_replace_all(location15,"San Mateo", "USA") 
location16
location17 <- str_replace_all(location16,"Chevy Chase", "USA") 
location17
location18 <- str_replace_all(location17,"Austin", "USA") 
location18
location19 <- str_replace_all(location18,"OR", "USA") 
location19
location20 <- str_replace_all(location19,"Boston", "USA") 
location20
location21 <- str_replace_all(location20,"sl", "SL") 
location21
location22 <- str_replace_all(location21,"Sri Lanka", "SL") 
location22
location23 <- str_replace_all(location22,"New Kensington", "USA") 
location23
location24 <- str_replace_all(location23,"Singaore", "Singapore") 
location24
location25 <- str_replace_all(location24,"US", "USA") 
location25
location26 <- str_replace_all(location25,"USAA", "USA") 
location26
location27 <- str_replace_all(location26,"NA", "USA") 
location27
location28 <- str_replace_all(location27,"Carfiff", "UK") 
location28
location29 <- str_replace_all(location28,"RO", "Romania") 
location29
location30 <- str_replace_all(location29,"England", "UK") 
location30
location31 <- str_replace_all(location30,"London", "UK") 
location31
location32 <- str_replace_all(location31,"IE", "Ireland") 
location32
location33 <- str_replace_all(location32,"ES", "Spain") 
location33
location34 <- str_replace_all(location33,"NC", "USA") 
location34
location35 <- str_replace_all(location34,"Colorado", "USA") 
location35
location36 <- str_replace_all(location35,"California", "USA") 
location36
```

```{r,echo=FALSE}
library(knitr)
kable(table(location36))
```
```{r,include=FALSE}
Location<-data.frame(table(location36))
Location
Direction<-data.frame(long=c(9.1021,133.775136,-51.92528,-106.346771,104.195397,9.9167,19.503304,78.96288,-8.24389,12.56738,138.252924,37.906193,101.975766,174.885971,121.774017,24.96676,105.318756,-3.188267,103.819836,79.861244,-3.703790,-3.435973,55.296249,97),lat=c(18.2812,-25.274398,-14.235004,56.130366,35.86166,51.5167,47.162494,20.593684,53.41291,41.87194,36.204824,-0.023559,4.210484,-40.900557,12.879721,45.943161,61.52401,55.953251,1.352083,6.927079,40.416775,55.378051,25.276987,38))
Direction
```

```{r,echo=FALSE,message=FALSE}
Location1<-cbind(Location,Direction)

attach(Location1)
world <- map_data("world")
mybreaks <- c(1, 10, 30, 50,105)
ggplot() +
  geom_polygon(data = world, aes(x=long, y = lat, group = group), fill="#DAA520", alpha=0.5,colour = "grey50") +
  geom_point(data=Location, aes(x=long, y=lat,size=Freq, color=Freq),stroke=F, alpha=2.5) +
  scale_size_continuous(name="Freq", trans="log", range=c(1,8),breaks=mybreaks, labels = c("0-2","3-10", "11-30", "29-50", "51-105")) +
  scale_color_viridis_c(option="inferno",name="Freq", trans="log",breaks=mybreaks, labels = c("0-2","3-10", "11-30", "29-50", "51-105")) +
  theme_void() + 
  guides( colour = guide_legend()) +
  labs(caption = "World Map of Company Locations") +
  theme(
    legend.position = "top",
    text = element_text(color = "#22211d"),
    plot.background = element_rect(fill = "#DAA520", color = "black"), 
    panel.background = element_rect(fill = "#ffffff", color = "black"), 
    legend.background = element_rect(fill = "#ffffff", color = "black")
  )
```

**We can colclude that based on the above world map its ilustrates that most of the company locations are situated in USA,Sri Lanka,India,Australia,Singapore,China and Canada.**

###Figure 04

###Multiple Bar Chart of Software Languages

```{r,include=FALSE}
library(tidyverse)
D <- str_to_lower(DSS1$R)
D1<- str_replace_all(D,"1", "Yes") 
D2<- str_replace_all(D1,"0", "No")

R<-na.omit(D2)
table(R)



E <- str_to_lower(DSS1$Python)
E1<- str_replace_all(E,"1", "Yes") 
E2<- str_replace_all(E1,"0", "No")
Python<-na.omit(E2)
table(Python)


F <- str_to_lower(DSS1$SQL)
F1<- str_replace_all(F,"1", "Yes") 
F2<- str_replace_all(F1,"0", "No")
SQL<-na.omit(F2)
table(SQL)

G <- str_to_lower(DSS1$`C++`)
G1<- str_replace_all(G,"1", "Yes") 
G2<- str_replace_all(G1,"0", "No")
`C++`<-na.omit(G2)
table(`C++`)

I <- str_to_lower(DSS1$C)
I1<- str_replace_all(I,"1", "Yes") 
I2<- str_replace_all(I1,"0", "No")
C<-na.omit(I2)
table(C)

J <- str_to_lower(DSS1$`C#`)
J1<- str_replace_all(J,"1", "Yes") 
J2<- str_replace_all(J1,"0", "No")
`C#`<-na.omit(J2)
table(`C#`)



```

```{r,include=FALSE}
Software_Languages <- c(rep("R" , 2) , rep("Python" , 2) , rep("SQL" , 2) , rep("`C++`" , 2), rep("C" , 2),rep("C#" , 2))

Status<-rep(c("Yes" , "No" ) , 6)

Frequency<-c(213,197,285,138,241,166,16,346,6,358,2,360)

data<-data.frame(Software_Languages,Status,Frequency)

```

```{r,echo=FALSE}
library(ggplot2)

ggplot(data, aes(fill=Status, y=Frequency, x=Software_Languages)) + 
  geom_bar(position="dodge", stat="identity",width=0.8)+ggtitle("Status of Software Languages")

```

**Above multiple bar chart illustrates that mostly required software languages are 'R','Python' and 'SQL'.**



##Flex Dashboard Content

(01). **Panel 01** = Bar Graph of Required Job Titles / Figure 01

(02). **Panel 02** = Word Cloud of Job Titles / Figure 02

(03). **Panel 03** = World Map of Company Locations / Figure 03

(04). **Panel 04** = Status of Software Languages / Figure 04 

